Discon analysis

### 2018-08-14 analysis/01_analysis.Rmd
recency experiment with 5,1,0

data <- raw_data %>%
  mutate(correct_target3 = ifelse(correct_target1 == 0 & correct_target2 == 0, 1, 0)) %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
         pick = ifelse(pickPos == "item_l", item_l, ifelse(pickPos == "item_r", item_r, ifelse(pickPos=="item_m", item_m, NA))),
         correct_item = ifelse(pick == correctItem, 1, 0),
         pickTest = substr(pick, 4, length(pick)),
         correct_target1 = ifelse(pickTest == target1, 1, 0),
         correct_target2 = ifelse(pickTest == target2, 1, 0),
         correct_target3 = ifelse(pickTest == target3, 1, 0))

write.csv(data, file="../data/pilot.data.csv")

@@

data <- data %>%
  filter(!workerid %in% drop)
```

```{r}
data %>%
  filter(phase == "test", distribution == "c(4, 2, 0)") %>%
  group_by(pickTest) %>%
  summarise(mean = mean(correct_target1))
```
# Do proportion of choices match the frequency in the distribution

@@

@@

```{r plot 2}
a <- data %>%
  filter(slide == 6) %>%
  select(workerid, pick)

b <- data %>%
  filter(slide == "choice") %>%
  select(workerid, distribution, pickTest, correct_target1)

@@

```{r}
data %>%
  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
  group_by(pick) %>%
  summarise(n = length(correct_target1),
            mean = mean(correct_target1)) %>%
  arrange(mean)
```

>>>>

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")))

 # data <- raw_data %>%
 #  mutate(correct_target3 = ifelse(correct_target1 == 0 & correct_target2 == 0, 1, 0)) %>%
 #  mutate(distribution = as.character(distribution),
 #         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
 #         pick = ifelse(pickPos == "item_l", item_l, ifelse(pickPos == "item_r", item_r, ifelse(pickPos=="item_m", item_m, NA))),
 #         correct_item = ifelse(pick == correctItem, 1, 0),
 #         pickTest = substr(pick, 4, length(pick)),
 #         correct_target1 = ifelse(pickTest == target1, 1, 0),
 #         correct_target2 = ifelse(pickTest == target2, 1, 0),
 #         correct_target3 = ifelse(pickTest == target3, 1, 0))

# write.csv(data, file="../data/pilot.data.csv")

@@

data <- data %>%
  filter(!workerid %in% drop)

# Some preliminary tests
```{r}
data_test <- data %>% 
  filter (phase == "test", distribution == "c(4, 2, 0)") %>%
  summarise (lastInput = mean(same_lastInput),
             n = length(distribution))
#23/38 trials

data_test <- data %>%
  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
  summarise (correct1 = mean(correct_target1))

data_test <- data %>%
  filter(phase == "test", distribution == "c(2, 2, 2)") %>%
  summarise (lastInput = mean(same_lastInput),
             n = length(distribution))
# 23/38

# Salience of each category
```{r}
plot1 <- data %>%
  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
  group_by(distribution, target1) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3))

plot1 <- data %>%
  filter(phase == "test", distribution == "c(6, 0, 0)", target1 == "vehicles")

# clothes: 2
# fruits: 5
# furniture: 10
# instruments: 4
# mammals: 8
# vehicles: 9

plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, target1) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -target1) %>%
  group_by(distribution, item, target1) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(target1~distribution) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```
# Do proportion of choices match the frequency in the distribution

@@

```
# How does the last item seen affect the object chosen in the anaphora case? 
```{r}
plot2 <- data %>%
  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
  group_by (distribution, workerid) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>% 
  multi_boot_standard(col = "lastInput")

plot2 <- data %>%
  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
  group_by (distribution, workerid) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>% 
  multi_boot_standard(col = "lastInput")

ggplot(plot2,
       aes(x = distribution, y = mean, fill = distribution)) +
  geom_bar(stat='identity', width = 0.3) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few()
```
# Does the graded distribution come through in cases where the last input does not affect the object choice?
```{r}
plot3 <- data %>%
  filter(phase == "test", distribution == "c(4, 2, 0)", same_lastInput == 0) %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot3,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

@@

```{r}
a <- data %>%
  filter(slide == 6) %>%
  select(workerid, pick)

b <- data %>%
  filter(slide == "choice") %>%
  select(workerid, distribution, pickCat, correct_target1)

@@
